##Data Load, Processing, and Exploration
###Load Data 
Perform data download and initial data load of the test and training data
```{r, cache=TRUE}
trainURL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
trainFile <- "pml-training.csv"
testURL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
testFile <- "pml-testing.csv"
download.file(trainURL, trainFile, method="curl")
download.file(testURL, testFile, method="curl")
train <- read.csv(trainFile,na.strings=c("NA",""))
test <-read.csv(testFile,na.strings=c("NA",""))
```
###Initial Data Exploration
```{r}
dim(test)
dim(train)
train[1:5,1:10]
str(train)
```
###Data Preperation
```{r}
#Count the number of NAs in traiing and test set
trainCols <- colSums(is.na(train))
testCols <- colSums(is.na(test))
trainNAs <- table(trainCols)
testNAs <- table(testCols)
#Number of variables with NAs in train set
trainNAs
#Number of variables with NAs in test set
testNAs
```

The results show that there are many columns with close to or only NA data in the data set.  The next step is to remove these columns from the data, alnog with removal of the following non-numeric columns:
Initial Row Index Column, user_name, raw_timestamp_part_1, raw_timestamp_part_2, cvtd_timestamp, new_window, & num_window

```{r}
trainNAColumns <- trainCols >= 19216
testNAColumns <- testCols >= 20
trainPro <- train[!trainNAColumns]
testPro <- test[!testNAColumns]
trainPro <- trainPro[, -(1:7)] 
testPro <- testPro[, -(1:7)]
```

Now that the training and test set data is correct, we go ahead and create a validation set from our training set.

```{r}
library(caret)
inTrain <- createDataPartition(y=trainPro$classe, p=0.7, list=FALSE)
training <- trainPro[inTrain,]
validation <- trainPro[inTrain,]
```

##Model
Here we will select the appropriate model for predicing the classe based on the features of the training data.

###Random Forest
We will use the Random Forest technique to derive our model
```{r}
modFit <- train(classe ~ ., data=training, method="rf",prox=TRUE)


