##Data Load, Processing, and Exploration
###Load Data 
Perform data download and initial data load of the test and training data
```{r, cache=TRUE}
trainURL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
trainFile <- "pml-training.csv"
testURL <- "https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
testFile <- "pml-testing.csv"
download.file(trainURL, trainFile, method="curl")
download.file(testURL, testFile, method="curl")
train <- read.csv(trainFile,na.strings=c("NA",""))
test <-read.csv(testFile,na.strings=c("NA",""))
```
###Initial Data Exploration
```{r}
dim(test)
dim(train)
train[1:5,1:10]
str(train)
```
###Data Preperation
```{r}
#Count the number of NAs in traiing and test set
trainCols <- colSums(is.na(train))
testCols <- colSums(is.na(test))
trainNAs <- table(trainCols)
testNAs <- table(testCols)
#Number of variables with NAs in train set
trainNAs
#Number of variables with NAs in test set
testNAs
```
The results show that there are many columns with close to or only NA data in the data set.  The next step is to remove these columns from the data
```{r}
trainNAColumns <- trainCols >= 19216
testNAColumns <- testCols >= 20
trainPro <- train[!trainNAColumns]
testPro <- test[!testNAColumns]